---
title: "BEST exploratory analysis"
author: "Juan Carlos Rocha"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(ggplot2)
require(network)
require(sna)
require(dplyr)
require(RColorBrewer)
require(GGally)
library(vegan)
library(cluster)
library(NbClust);library(kohonen)
library(mclust); library(clValid)
```

## BEST: Behavioural Economics for Social-Ecological Systems with Thresholds

The **BEST** project aims to understand what are the behavioural responses of people who rely on natural resources for their livelihood, and whose resources could potentially present threshold like dynamics, aka. *"regime shifts"*. For this study we designed a game played with fishermen in four communities of the Colombian caribbean. Here I present a short exploration of the game data and survey.

### 

You can include R code in the document as follows:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
